---
title: "Critical Assessment of CAFA confidence prediction"
author: "Naihui Zhou"
date: "May 31, 2016"
output: pdf_document
---
```{r,echo=FALSE}
conv<-function(conf){
  if (conf=="True") return(1)
  else return(0)
}
read<-function(filepath){
  conf = read.table(filepath,sep="\t")
  conf[,1] = as.numeric(conf[,1])
  temp = unlist(strsplit(filepath,"/"))
  filename = temp[length(temp)]
  filename = unlist(strsplit(filename,'\\.'))[1]
  return(list(conf,filename))
}
getConf1<-function(conf,filename,tp,fp){
  #first figure
  par(mfrow = c(2,1))
  hist(tp[,1],breaks = 200, main = filename,probability = F,xlab = "true positives")
  hist(fp[,1],breaks = 200,main = NA,probability = F,xlab = "false positives")
}
getConf2<-function(conf,filename,tp,fp){
  par(mfrow = c(1,1))
  #second figure
  boxplot(tp[,1],fp[,1],names = c("True postives","False postives"),ylab="Confidence",main=filename)
  newcol = unlist(lapply(conf[,2], FUN=conv))
  newconf = cbind(conf,newcol)
  mse = sum((newconf[,1]-newconf[,3])^2)/nrow(conf)
  return (mse)
}
```

Team Name: Paccanaro Lab\par
Model: 1\par
BPO ranking: 1\par

```{r,echo=FALSE,warning=FALSE}
conf = read('/home/nzhou/git/CAFAAssess/confidence/85/tianlab_1_9606_BPO_confdata.txt')
confdata = conf[[1]]
name = conf[[2]]
tp = confdata[confdata[,2]=="True",]
fp = confdata[confdata[,2]=="False",]
getConf1(confdata,name,tp,fp)
```
```{r,warning=FALSE}

summary(tp[,1])
summary(fp[,1])
t.test(tp[,1],fp[,1],alternative = "g")
ks.test(tp[,1],fp[,1],alternative = "l")
```
```{r,echo=FALSE}
mse = getConf2(confdata,name,tp,fp)
```
\par
MSE(mean squared error):`r mse`
\newpage

Team Name: Tian Lab\par
Model: 1\par
BPO ranking: 2\par

```{r,echo=FALSE,warning=FALSE}
conf = read('/home/nzhou/git/CAFAAssess/confidence/85/tianlab_1_9606_BPO_confdata.txt')
confdata = conf[[1]]
name = conf[[2]]
tp = confdata[confdata[,2]=="True",]
fp = confdata[confdata[,2]=="False",]
getConf1(confdata,name,tp,fp)
```
```{r,warning=FALSE}

summary(tp[,1])
summary(fp[,1])
#t.test(tp[,1],fp[,1],alternative = "g")
ks.test(tp[,1],fp[,1],alternative = "l")
```
```{r,echo=FALSE}
mse = getConf2(confdata,name,tp,fp)
```
\par
MSE(mean squared error):`r mse`

\newpage
Team Name: MS -kNN\par
Model: 1\par
BPO ranking: 3\par

```{r,echo=FALSE,warning=FALSE}
conf = read('/home/nzhou/git/CAFAAssess/confidence/129/tu_1_9606_BPO_confdata.txt')
confdata = conf[[1]]
name = conf[[2]]
tp = confdata[confdata[,2]=="True",]
fp = confdata[confdata[,2]=="False",]
getConf1(confdata,name,tp,fp)
```
```{r,warning=FALSE}

summary(tp[,1])
summary(fp[,1])
#t.test(tp[,1],fp[,1],alternative = "g")
ks.test(tp[,1],fp[,1],alternative = "l")
```
```{r,echo=FALSE}
mse = getConf2(confdata,name,tp,fp)
```
\par
MSE(mean squared error):`r mse`



\newpage
Team Name: BLAST\par
Model: 1\par
BPO ranking: \par

```{r,echo=FALSE,warning=FALSE}
conf = read('/home/nzhou/git/CAFAAssess/confidence/BLAST/BB4S_bpo_confdata.txt')
confdata = conf[[1]]
name = conf[[2]]
tp = confdata[confdata[,2]=="True",]
fp = confdata[confdata[,2]=="False",]
getConf1(confdata,name,tp,fp)
```
```{r,warning=FALSE}

summary(tp[,1])
summary(fp[,1])
#t.test(tp[,1],fp[,1],alternative = "g")
ks.test(tp[,1],fp[,1],alternative = "l")
```
```{r,echo=FALSE}
mse = getConf2(confdata,name,tp,fp)
```
\par
MSE(mean squared error):`r mse`



\newpage
Team Name: Naive\par
Model: \par
BPO ranking: \par

```{r,echo=FALSE,warning=FALSE}
conf = read('/home/nzhou/git/CAFAAssess/confidence/Naive/BN4S_bpo_confdata.txt')
confdata = conf[[1]]
name = conf[[2]]
tp = confdata[confdata[,2]=="True",]
fp = confdata[confdata[,2]=="False",]
getConf1(confdata,name,tp,fp)
```
```{r,warning=FALSE}

summary(tp[,1])
summary(fp[,1])
#t.test(tp[,1],fp[,1],alternative = "g")
ks.test(tp[,1],fp[,1],alternative = "l")
```
```{r,echo=FALSE}
mse = getConf2(confdata,name,tp,fp)
```
\par
MSE(mean squared error):`r mse`
